Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-25 paper/aldebaran.tex
transits

>>>>

It would be a cruel conspiracy of nature if red giants support a type of oscillation which is common and closely resembles a planetary signal. We believe this cannot be the case: the populations of planets around subgiants and giants evolved from intermediate mass stars are similar \citep{2014A&A...566A.113J}, as expected if subgiants evolve into giants and retain their planetary systems in a similar configuration, and with very different stellar structures subgiants and giants are unlikely to share similar modes of long-period pulsation. The similarity of distributions of systems hosted by subgiant and giants could not be reproduced if a large fraction of the giants' planets were false positives. Moreover giant planets are expected to be common around intermediate-mass stars \citep{2008ApJ...673..502K}, and some are definitely known to be bona fide planets because they transit their star \citep[e.g.][]{2014A&A...562A.109L,2015A&A...573L...6O,2016AJ....152..185G,2017AJ....154..254G}.
